Universal Anonymous Signatures

### 2022-05-02 prism-backend/research/gsac/model-gsac.tex
Proofs for GSAC done (except correctnes...)
Some intro text.

\begin{definition}{(Correctness of \GSAC)}
  \label{def:correctness-gsac}
  A \GSAC scheme is correct if, for any p.p.t. adversary $\adv$, \ExpGSACCorrect
  outputs 1 with negligible probability.
\end{definition}

@@

\todo{Correctness definition.}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\DAttrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU, \nexists (\uid,\cdot,\Attrs) \in
    \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

@@

\paragraph{Discussion.} %
\todo{Modelling choices: HU and CU lists are typically updated in join protocols
  in the GS literature. Here, it is best to follow the AC literature, as a same
  user (key) may be associated to multiple join protocols. So there are HUGEN
  and CUGEN oracles.}

@@

\todo{Argue that our properties cover (and augment) a direct combination
  (even if possible) of their GS and AC counterparts. Specifically, anonymity
  of \GSAC is stronger than anonymity in GS and AC, and the same for trace and
  non-frame.}

\todo{It would be nice to prove that a \GSAC scheme to which we remove the
  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
  where all credentials have no attributes, and where we restrict to only
  one credential per user, becomes a conventional GS scheme.}

>>>>

\begin{definition}{(Correctness of \GSAC)}
  \label{def:correctness-gsac}
  A \GSAC scheme is correct if, for any p.p.t. adversary $\adv$,
  $\Pr[\ExpGSACCorrect(1^\secpar) = 1]$ is a negligible function of \secpar.
\end{definition}

@@

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpGSACTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\ipk,\isk) \gets \IKeyGen(\parm);~(\opk,\osk) \gets \OKeyGen(\parm);~ 
    \gpk \gets (\ipk,\opk) \\
    (\sig,\DAttrs,\msg) \gets
    \adv^{\HUGEN,\CUGEN,\RREG,\OBTISS,\ISSUE,\SIGN,\OPEN}(\gpk,\osk) \\
    \pcif \Verify(\gpk,\sig,\DAttrs,\msg) = 0: \pcreturn 0 \\
    \pcif \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) = \bot: \pcreturn 1 \\
    \textrm{Let}~(\upk,\oproof) \gets \Open(\gpk,\osk,\trans,\sig,\DAttrs,\msg) \\
    \pcif \Judge(\gpk,\upk,\oproof,\sig,\DAttrs,\msg) = 0: \pcreturn 1 \\
    \pcelse \pcif \forall \uid \in \CU \cup \HU, \nexists (\uid,\cdot,\Attrs)
    \in \CRED~\st~\DAttrs \subseteq \Attrs: \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Traceability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-trace}
\end{figure}

@@

\subsubsection{A note comparing \GSAC with group signatures and
  anonymous credentials.} %

\GSAC is a direct combination of group signatures and anonymous credentials.
%
On the one hand, by restricting to credentials without attributes (i.e., where
the only attribute is the user secret key), we get a vanilla group signature
scheme. Although, strictly, our scheme allows users to fetch more than one
credential -- which goes beyond vanilla group signatures -- this can be
trivially ``compensated'' by requiring users to prove ownership of a
conventional digital identity during the $\langle \Obtain,\Issue \rangle$
protocol\footnote{This is indeed common practice, but also frequently ommitted
  in research papers.}.
%
On the other hand, by instantiating a \GSAC scheme (e.g., as \GSACGen) and simply
throwing out the opener's key pair (thus, making \Open and \Judge useless), one
gets a vanilla anonymous credential system. Or, keeping \osk, one can build an
anonymous credential system with blacklisting, which can be directly built via
the \Open function.

\todo{Can we do formal proofs here of $GSAC \implies$ GS and $GSAC \implies AC$?}

\iffalse
\todo{Modelling choices: HU and CU lists are typically updated in join protocols
  in the GS literature. Here, it is best to follow the AC literature, as a same
  user (key) may be associated to multiple join protocols. So there are HUGEN
  and CUGEN oracles.}

@@

\todo{It would be nice to prove that a \GSAC scheme to which we remove the
  \Open/\Judge functions becomes an AC scheme. And conversely, a \GSAC scheme
  where all credentials have no attributes, and where we restrict to only
  one credential per user, becomes a conventional GS scheme.}
\fi

### 2022-05-02 prism-backend/research/gsac/sec-gsac.tex
Generic GSAC construction. Some reorganisation.
Some intro text.

\todo{Some intro here}

\input{model-gsac.tex}
\input{construction-gsac.tex}

>>>>

\todo{I think we should extend ``vanilla'' \GSAC to return the full \Attrs
  in \Open, but without needing \trans as a parameter to \Open (for compatibility
  with \UAS). This can be done by encrypting all attributes, including their
  ciphertext in the signature, and proving they are part of the credential. This
  would render the scheme too costly, but helps in arguing in favour of \UAS.}

Before moving into our full-fledged scheme for universal anonymous signatures,
we take a first step which, albeit somehow obvious and simple, helps understand
our final goal. Namely, we give a scheme that combines in a quite direct manner
the functionality of group signature schemes, and that of anonymous credential
schemes.

\paragraph{Why is this merge necessary in the real world?} %
Despite being an \emph{a priori} simple combination of both schemes we argue
that such a combination:

\begin{itemize}
\item Enables a natural way to incorporate accountability within 
  privacy-preserving identities. Furthermore, it does so in a formal way,
  via the traceability notion and, crucially, the non-frameability one,
  (which is not present in anonymous credentials).
\item Provides meaning to the conventional \Open functionality of group
  signatures, which traditionally has only required that an abstract concept of
  ``identity'' be returned. Concretely, assuming honest issuance (which is
  already a requirement in anonymous credentials; and in group signatures for
  traceability), we can make specific claims about the attributes associated to
  de-anonymized signers. Otherwise, without integrating attributes within the
  issued credentials, the value returned by \Open serves barely for blacklisting
  or similar functionalities -- but otherwise gives no information straight away
  about the signer's identity, forcing implementors to rely to non-cryptographic
  means to retrieve such information.
\end{itemize}

\paragraph{Intuition of our design and construction.} %
Functionally, we combine both worlds. Namely, a user can get as many credentials
as s/he wants -- although all are tied to the same user key --, and signatures
(or credential presentations) of the same credential must be unlinkable. In this
simplified first step, we restrict to selective attribute disclosure, meaning
that signatures produced by a credential reveal only a subset of the attributes
in that credential. Given such a signature, there is a trusted opener who can
de-anonymize its signer, producing back its public key, as well as a proof of
correct opening.

With respect to the model, privacy-wise this direct combination requires that
any two signatures (credential presentations) reveal nothing about the
credential used to produce them, beyond the revealed attributes. For this first
step, security-wise we stick to the conventional separation of
unforgeability-related properties in group signatures. That is, traceability
requires that, in the presence of an honest issuer, all valid signatures must
originate from a credential issued by the issuer; and, moreover, that no
user can claim having attributes that have not been issued to a single
credential. As in group signatures, if the issuer is corrupt, all we can hope
for is that honest users do not get undeserved blame; but, other than that,
the adversary can obviously obtain credentials with arbitrary attributes. Still,
note that this is a clear gain with respect to conventional anonymous credential
systems, which offer no security against a malicious issuer.

Finally, in this first step, we restrict ourselves to signatures/presentations
involving only one credential and, as stated, to selective attribute disclosure.

\input{model-gsac.tex}
\input{construction-gsac.tex}
\input{security-gsac.tex}
